Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-19 paper/icml_drau/experiments.tex

\paragraph{Qualitative experiments: Visualizing policies and values}
To provide qualitative results, and check that robustness to time
discretization is provided both in term of raw return results, but also in term
of convergence of approximate value function and policies, we first provide results on the simple pendulum environment
from the OpenAI Gym classic control suite.  This environment's state space is of dimension $2$. A visualization of both the learnt value and policy functions is obtained by plotting for each point of the phase diagram $(\theta, \dot{\theta})$ its value and policy. results are presented in
Fig.~\ref{fig:pend} for the policy function and in Fig.\TODO{ref} in Supplementary \TODO{ref} for the value function.

>>>>

\paragraph{Qualitative experiments: Visualizing policies and values.}
To provide qualitative results, and check robustness to time
discretization both in terms of raw return results and in terms
of convergence of the approximate value function and policies, we first provide results on the simple pendulum environment
from the OpenAI Gym classic control suite.  Its state space is of
dimension $2$. We visualize both the learnt value and policy functions by
plotting, for each point of the phase diagram $(\theta, \dot{\theta})$,
its value and policy. The results are presented in
Fig.~\ref{fig:pend} for the policy function and in Fig.\TODO{ref} in Supplementary \TODO{ref} for the value function.
